### 2015-06-16 reports/paper/conclusion.tex
thesis

For future directions, one can extend the system with another microphone on each array to perform 3D localization. However, the number of grid points increases exponentially with the number of dimension, which means the calculation time also increases exponentially. Therefore, it is important to research more efficient ways to find the intersection of hyperbolic cones the in 3D space.  Since the likelihood calculation on each grid point is independent of each other, one straightforward way to speedup calculation is to employ hardware accelerated parallel computing technologies such as GPU or FPGA. Another useful direction is to investigate multi-source localization using digitally tagged audio sources.

>>>>

For future directions, one can extend the system with another microphone on each array to perform 3D localization. However, the number of grid points increases exponentially with the number of dimensions, which translates into exponential increase in computation time. To keep the localization in real time (time lag of less than $0.1$ seconds), it is important to research more efficient ways of finding the intersection of hyperbolic cones the in the 3D space. Since the likelihood calculation on each grid point is simply a look up on the cross-correlation output from each microphone pair, the computation at each grid point is independent of each other. Therefore, One straightforward way to speedup calculation is to employ hardware accelerated parallel computing technologies such as GPU or FPGA.

Another direction is to investigate multi-source localization. One approach is to allocate different frequency bands to difference sound sources. However, the number of frequency bands are limited in the audible audio spectrum. The arrival time difference estimation is also more immune to noise for wider band audio sources. A different approach is to digitally encode and tag the audio source. Different sources can be differentiated if each source uses a waveform that has a different digital signature.

### 2015-06-16 reports/paper/experiment.tex
thesis

\section{Results}
\subsection{Point localization}
To test how accuracy varies with window size, the algorithm is fed with microphone data of different lengths, and the result is shown in fig~\ref{fig:accuracy_vs_window}. The error decreases as window size increases and plateaus after the window size exceeds around $10$ millisecond. The lowest error achieved is $2.53$ centimeters, which occurred when the window size is set to 12 millisecond and GCC\_PHAT is used for TDOA estimation.

@@

Fig~\ref{fig:wn} gives an intuitive representation of how accuracy changes with window size. When window size is small ($1.02$ millisecond), the audio does not contain enough information to reliably estimate TDOA, which results in noisy localization. As window size increases, localization converges to the shape of the ground truth circle. Fig~\ref{fig:err_win_circle} shows how the error changes with window size. The general trend is similar to that in point localization case. Error decreases as the window size increases and plateaus after it exceeds around $10$ milliseconds.

@@

Fig~\ref{fig:circle_wnn} to \ref{fig:circle_musicbn} shows results for experiments at normal speed, and Fig~\ref{fig:circle_wnf} to~\ref{fig:circle_musicbf} shows results at fast speed. By comparing localization error for each audio source between normal movement speed and fast movement speed, we find that localization error does not depend on how fast the sound source is moving. For example fig~\ref{fig:circle_musican} and fig~\ref{fig:circle_musicaf} shows that localization error is $1.289$ cm at normal movement speed and $1.291$ cm at fast movement speed.

For normal speed movement tracking, localization error is $0.9$ cm for white noise, $1.29$ cm for Music A, and $2.9$ cm for Music B. Localization accuracy is the best for white noise source, and worst for Music B. This is consistent with our expectation because low amplitude regions in Music B would cause arrays to lose track of where the source is. This can also be seen from the ``blank'' regions in fig~\ref{fig:circle_musicbn}.

It also shows that raw detection has the most amount of jiggling. Kalman filter reduces the amount of jiggling from raw detection. Averaging filter has the least amount of jiggling. However, averaging filter averages detection outputs from past 0.5 seconds, which makes the filtered output lag the real movement.

>>>>

\section{Results}
\subsection{Point localization}
To test how accuracy varies with window size, the algorithm is fed with microphone data of different lengths, and the result is shown in fig~\ref{fig:accuracy_vs_window}. The error decreases as window size increases and plateaus after the window size exceeds around $10$ millisecond. The lowest error achieved is $2.53$ centimeters, which occurred when the window size is set to 12 millisecond and GCC\_PHAT is used for TDOA estimation. The performance differences among GCC, GCC\_PHAT and GCC\_PHAT\_SQRT is small.

@@

Fig~\ref{fig:wn} gives an intuitive representation of how accuracy changes with window size. When window size is small ($1.02$ millisecond), the audio does not contain enough information to reliably estimate TDOA, which results in noisy localization. As window size increases, the TDOA estimation becomes more accurate and the localization converges to the shape of the ground truth circle. Fig~\ref{fig:err_win_circle} shows how the error changes with window size. The general trend is similar to that in point localization case. Error decreases as the window size increases and plateaus after it exceeds around $10$ milliseconds.

@@

Fig~\ref{fig:circle_wnn} to \ref{fig:circle_musicbn} shows results for experiments at normal speed, and Fig~\ref{fig:circle_wnf} to~\ref{fig:circle_musicbf} shows results at fast speed. By comparing localization error for each audio source between normal movement speed and fast movement speed, we find that localization error does not increase when the source movement speed increased from $10$ cm to $20$ cm. For example fig~\ref{fig:circle_musican} and fig~\ref{fig:circle_musicaf} shows that localization error is $1.289$ cm at normal movement speed and $1.291$ cm at fast movement speed.

For normal speed movement tracking, localization error is $0.9$ cm for white noise (Fig~\ref{fig:circle_wnn}), $1.29$ cm for Music A (Fig~\ref{fig:circle_musican}), and $2.9$ cm for Music B (Fig~\ref{fig:circle_musicbn}). Localization accuracy is the best for white noise source, and worst for Music B. This is consistent with our expectation because low amplitude regions in Music B would cause arrays to lose track of where the source is. This can also be seen from the ``blank'' regions in fig~\ref{fig:circle_musicbn}.

It also shows that raw detection has the most amount of jiggling. Kalman filter reduces the amount of jiggling from raw detection by combining past estimates with current estimates. Averaging filter has the least amount of jiggling. However, averaging filter averages detection outputs from past 0.5 seconds, which makes the filtered output lag the real movement.

### 2015-06-16 reports/paper/introduction.tex
thesis

Accurate indoor localization allows creation of novel applications with surrounding awareness that uses position and movement information as input. One application is to allow users to draw with music without physically touching the computer. Another example is to build AI games with physical pieces such as toy car racing where the computer controls some of the toy cars. In this work, we aim to build such a source localization system that is portable, inexpensive, yet reasonably accurate for localization in a small area.

@@

In this project, we have built a localization system with reasonably high precision for small area using microphone arrays that localize typical audio sources. Our system is built with inexpensive electret microphones mounted on portable frames. Users can interact with our system using any device that has audio output such as a mobile phone.

>>>>

Accurate indoor localization allows creation of novel applications with surrounding awareness that uses position and movement information as input.

@@

In this work, we have built a source localization system that is portable, inexpensive, yet reasonably accurate for localization in a small area. Our system is built with inexpensive electret microphones mounted on portable frames. Users can interact with our system using any device that has audio output such as a mobile phone.

This system can be used in Human-Computer Interaction (HCI) applications that incorporate sound position and movement information. One can use this system to build virtual drawing applications where the user can draw with music without physically touching the computer. One can also use this system to design interactive AI games with physical pieces. For example, a chess game with physical pieces can be developed where each piece is equipped with a motor and a music tag. Since the computer knows where all the pieces are and where the user has moved, it can make its corresponding move. Another similar example is to build an AI toy car racing game, where the player controls one car and the computer controls another. With real time location information, the computer can compete with the player on a racing track.

This system can also be used to in Augmented Reality (AR) applications. For example, the user can wear a music tag on the finger, and then the system would be able to track the finger movement. this particular setup can be used as a virtual mouse for wearable technologies such as Google Glass.

### 2015-06-16 reports/paper/prior.tex
thesis

For a point sound source in a direct field, the signal intensity decays proportional to the square of the distance between the source and the microphone. Let $I_i$ denote the received signal intensity at microphone $i$: 
\[
I_i \propto \frac{1}{d_i^2} I_s
\]
where $d_i$ is the distance between the audio source and microphone $i$, and $I_s$ is the sound intensity at the source.
With two microphones, the signal intensity received at both microphones has to satisfy equation~\ref{eqn:ild1}:
\begin{eqnarray}
I_1d_1^2 &=& I_2d_2^2\\
\label{eqn:ild}
\frac{I_1}{I_2} &=& \frac{d_2^2}{d_1^2}
\end{eqnarray}
It can be shown that, on a 2D plane, points satisfy equation~\ref{eqn:ild} form a circle when $I_1 \ne I_2$ and form a line when $I_1 = I_2$~\cite{ild:1}. With two microphones all points on this curve generate the same intensity ratio and can not be distinguished from each other. Multiple approaches have been investigated to eliminate this ambiguity. \cite{ild:1} employed multiple microphones and used the intersection of circles from each microphone pair to estimate the source location. \cite{ild:3} combined ILD with Interaural Time Difference (ITD) to estimate the source direction (i.e azimuth). Instead of solving the intersection of circles, \cite{ild:4} employed machine learning techniques to automatically learn the mapping from ILD and ITD features to location coordinate. It uses four microphones and requires a training phase, during which the sound source is manually placed at predetermined locations for the system to learn the parameters that map from feature space to the sound location.

@@

Cross-correlation has also been used to measure signal arrival time differences\cite{tdoa:mit2, tdoa:micloc, tdoa:3}. Cross correlation is a measure of similarity between two signals. For real valued signals $x_1(t)$, $x_2(t)$ a time shift $\tau$:
\begin{eqnarray}\label{eqn:gcc0}
\mbox{xcorr}_{x_1,x_2}(\tau) = \int_{-\infty}^{\infty} x_1(t) x_2(t+\tau)dt
\end{eqnarray}
We can take Fourier Transform on both sides of equation~\ref{eqn:gcc0}:
\begin{eqnarray}\label{eqn:gcc1}
\mathcal{F}\{\mbox{xcorr}_{x_1,x_2}(\tau)\} & = & X_1(\omega) X_2(-\omega)\\
& =& X_1(\omega) X_2(\omega)^*
\end{eqnarray}
Where $X_1(\omega)$ and $X_2(\omega)$ are the Fourier Transforms of $x_1(t)$ and $x_2(t)$. We can retrieve the cross-correlation result in time domain by taking inverse Fourier transform:
\begin{eqnarray}\label{eqn:gcc2}
\mbox{xcorr}_{x_1,x_2}(\tau) = \int_{-\infty}^\infty X_1(\omega)X_2(\omega)^*e^{j\omega\tau} d\omega
\end{eqnarray}
The arrival time difference $t_0$ is the time shift $\tau$ that maximizes~\ref{eqn:gcc2}:
\begin{eqnarray}\label{eqn:gcc3}
t_0 = \arg\max_\tau\mbox{xcorr}_{x_1,x_2}(\tau) 
\end{eqnarray}

@@

To see the reasoning behind different prefiltering approaches, we separate the magnitude part from the phase part of $X_1(\omega)$ and $X_2(\omega)$ in Equation~\ref{eq:gcc2}:
\begin{eqnarray}
\label{eqn:phat1}
R_{x_1x_2}(\tau) &=& \int_{-\infty}^\infty W(\omega) |X_1(\omega)||X_2(\omega)| e^{j(\omega\tau - (\angle{X_2(\omega)} - \angle{X_1(\omega)}) } d\omega\\
&=& \int_{-\infty}^\infty \underbrace{W(w)|X_1(\omega)| |X_2(\omega)|}_{\mbox{weighting}} \cos(\Theta_\epsilon) d\omega
\end{eqnarray}
Where $\Theta_{e}$ is the phase error:
\[
\Theta_\epsilon = \omega\tau - (\angle X_2(\omega) - \angle X_1(\omega))
\]
We can look at the real part of equation~\ref{eqn:phat1} only since both $x_1(t)$ and $x_2(t)$ are real valued signals. When $\dot \tau$ is the true arrival time difference between $x_1(t)$ and $x_2(t)$, phase error $\Theta_\epsilon  = 0$, and $\cos(\Theta_\epsilon) = 1$. When $\dot \tau$ differs from the true arrival time difference, $\cos(\Theta_\epsilon) < 1$. Therefore, $\cos(\Theta_\epsilon)$ can be seen as a measure of the phase error, and $W(w)|X_1(\omega)||X_2(\omega)|$ describes how the error should be weighted at each frequency. The TDOA estimator essentially sums the weighted phase error at each frequency.

>>>>

For a point sound source in a direct field, the signal intensity decays proportional to the square of the distance between the source and the microphone. Let $I_i$ denote the received signal intensity at microphone $i$: 
\begin{eqnarray}\label{eqn:ild1}
I_i \propto \frac{1}{d_i^2} I_s
\end{eqnarray}
where $d_i$ is the distance between the audio source and microphone $i$, and $I_s$ is the sound intensity at the source.
With two microphones, the signal intensity received at both microphones has to satisfy equation~\ref{eqn:ild1}:
\begin{eqnarray}
I_1d_1^2 &=& I_2d_2^2\\
\label{eqn:ild}
\frac{I_1}{I_2} &=& \frac{d_2^2}{d_1^2}
\end{eqnarray}
It can be shown that, on a 2D plane, points satisfy equation~\ref{eqn:ild} form a circle when $I_1 \ne I_2$ and form a line when $I_1 = I_2$~\cite{ild:1}. With two microphones all points on this curve generate the same intensity ratio and can not be distinguished from each other. Multiple approaches have been investigated to eliminate this ambiguity. \cite{ild:1} employed multiple microphones and used the intersection of circles from each microphone pair to estimate the source location. \cite{ild:3} combined ILD with Interaural Time Difference (ITD) to estimate the source direction (i.e azimuth). Instead of solving the intersection of circles, \cite{ild:4} employed machine learning techniques to automatically learn the mapping from ILD and ITD features to location coordinate. It uses four microphones and requires a training phase, during which the sound source is manually placed at predetermined locations for the system to learn the parameters that map from feature space to the sound location.

@@

Cross-correlation has also been used to measure signal arrival time differences\cite{tdoa:mit2, tdoa:micloc, tdoa:3}. Cross correlation is a measure of similarity between two signals. For real valued signals $x_1(t)$ and $x_2(t)$, the cross-correlation between them at a particular time shift $\tau$ can be calculated as:
\begin{eqnarray}\label{eqn:gcc0}
 R_{x_1,x_2}(\tau) = \int_{-\infty}^{\infty} x_1(t) x_2(t+\tau)dt
\end{eqnarray}
We can take Fourier Transform on both sides of equation~\ref{eqn:gcc0}:
\begin{eqnarray}\label{eqn:gcc1}
\mathcal{F}\{ R_{x_1,x_2}(\tau)\} & = & X_1(\omega) X_2(-\omega)\\
& =& X_1(\omega) X_2(\omega)^*
\end{eqnarray}
Where $X_1(\omega)$ and $X_2(\omega)$ are the Fourier Transforms of $x_1(t)$ and $x_2(t)$. We can retrieve the cross-correlation result in time domain by taking inverse Fourier transform:
\begin{eqnarray}\label{eqn:gcc2}
 R_{x_1,x_2}(\tau) = \int_{-\infty}^\infty X_1(\omega)X_2(\omega)^*e^{j\omega\tau} d\omega
\end{eqnarray}
The arrival time difference $t_0$ is the time shift $\tau$ that maximizes~\ref{eqn:gcc2}:
\begin{eqnarray}\label{eqn:gcc3}
t_0 = \arg\max_\tau R_{x_1,x_2}(\tau) 
\end{eqnarray}

@@

To see the reasoning behind different prefiltering approaches, we separate the magnitude part from the phase part of $X_1(\omega)$ and $X_2(\omega)$ in Equation~\ref{eq:gcc2}:
\begin{eqnarray}
\label{eqn:phat1}
R_{x_1x_2}(\tau) &=& \int_{-\infty}^\infty W(\omega) |X_1(\omega)||X_2(\omega)| e^{j(\omega\tau - (\angle{X_2(\omega)} - \angle{X_1(\omega)}) } d\omega\\
&=& \int_{-\infty}^\infty \underbrace{W(w)|X_1(\omega)| |X_2(\omega)|}_{\mbox{weighting}} \cos(\Theta_\epsilon) d\omega
\end{eqnarray}
Where $\Theta_{e}$ is the phase error:
\[
\Theta_\epsilon = \omega\tau - (\angle X_2(\omega) - \angle X_1(\omega))
\]
We can look at the real part of equation~\ref{eqn:phat1} only since both $x_1(t)$ and $x_2(t)$ are real valued signals. When $\tau$ is the true arrival time difference between $x_1(t)$ and $x_2(t)$, phase error $\Theta_\epsilon  = 0$, and $\cos(\Theta_\epsilon) = 1$. When $\tau$ differs from the true arrival time difference, $\cos(\Theta_\epsilon) < 1$. Therefore, $\cos(\Theta_\epsilon)$ can be seen as a measure of the phase error, and $W(w)|X_1(\omega)||X_2(\omega)|$ describes how the error should be weighted at each frequency. The TDOA estimator essentially sums the weighted phase error at each frequency.

### 2015-06-16 reports/paper/simulation.tex
thesis update
thesis

\begin{figure}[]
  \centering
  \begin{subfigure}[]{.46\textwidth}
    \includegraphics[width=\textwidth]{sim/sim_2_1}
    \caption{source at $(r=50$ cm, $\theta = 0$ degrees$)$}
  \end{subfigure}
  \begin{subfigure}[]{.46\textwidth}
    \includegraphics[width=\textwidth]{sim/sim_2_2}
    \caption{source at $(r=50$ cm, $\theta = 45$ degrees$)$}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/sim_2_3}
%    \caption{source at $(r=50$ cm, $\theta = 90$ degrees$)$}
%  \end{subfigure}
  \caption{Uncertainty region. Yellow dots represent microphones' locations and the white dot represents the location of the source.}
  \label{fig:sim_2_5}
\end{figure}

@@

\begin{figure*}[]
  \centering
  \begin{subfigure}[]{.46\textwidth}
    \includegraphics[width=\textwidth]{sim/result_20cm_0_degrees}
    \caption{0 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_20cm_45_degrees}
%    \caption{45 degrees}
%  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_20cm_90_degrees}
%    \caption{90 degrees}
%  \end{subfigure}
  \begin{subfigure}[]{.46\textwidth}
    \includegraphics[width=\textwidth]{sim/result_20cm_135_degrees}
    \caption{135 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_20cm_180_degrees}
%    \caption{180 degrees}
%  \end{subfigure}
  \caption{Uncertainty region. Microphones are at the vertices of a $20$cm equilateral triangle. The source is $20$cm away from the array.}
  \label{fig:sim_3_2}
\end{figure*}

\begin{figure*}[]
  \centering
  \begin{subfigure}[]{.46\textwidth}
    \includegraphics[width=\textwidth]{sim/result_80cm_0_degrees}
    \caption{0 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_80cm_45_degrees}
%    \caption{45 degrees}
%  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_80cm_90_degrees}
%    \caption{90 degrees}
%  \end{subfigure}
  \begin{subfigure}[]{.46\textwidth}
    \includegraphics[width=\textwidth]{sim/result_80cm_135_degrees}
    \caption{135 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_80cm_180_degrees}
%    \caption{180 degrees}
%  \end{subfigure}
  \caption{Uncertainty region. Microphones are at the vertices of a $20$cm equilateral triangle. The source is $80$cm away from the array.}
  \label{fig:sim_3_8}
\end{figure*}

@@

\begin{figure*}[]
  \centering
  \begin{subfigure}[]{.3\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_center}
    \caption{$3$ microphones are placed at vertices of a $20$cm equilateral triangle. The average error is $18.6$ cm}
    \label{fig:sim_hm_3}
  \end{subfigure}
  \begin{subfigure}[]{.3\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_p1}
    \caption{Another microphone is added at origin. The average error is $17.1$ cm}
    \label{fig:sim_hm_3_p1}
  \end{subfigure}
  \begin{subfigure}[]{.3\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_2x}
    \caption{$3$ microphones are placed at vertices of a $40$cm equilateral triangle. The average error is $10.04$ cm}
    \label{fig:sim_hm_3_2x}
  \end{subfigure}
  \begin{subfigure}[]{.3\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_line}
    \caption{$3$ microphones are placed in a line, $10$ cm apart from each other. The average error is $55.05$ cm}
    \label{fig:sim_hm_3_line}
  \end{subfigure}
  \begin{subfigure}[]{.3\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_4corner}
    \caption{$4$ microphones are placed at $4$ corners of the grid. The average error is $0.05$ cm}
    \label{fig:sim_hm_4}
  \end{subfigure}
  \begin{subfigure}[]{.3\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_2a}
    \caption{Two $3$ microphone arrays are placed $1$ meter apart. The average error is $2.60$ cm}
    \label{fig:sim_hm_2_array}
  \end{subfigure}
  \caption{Error heatmap for different array configurations. The heatmap scale is the intersection area measured in $cm^2$}.
  \label{fig:sim_hm}
\end{figure*}

@@

To evaluate how adding one microphone (without increasing the array size) improves accuracy, another microphone is added to the array at $(0,0)$. Result is presented in fig~\ref{fig:sim_hm_3_p1}. Addition of the new microphone only slightly improved the accuracy around the array region. The average error dropped from $18.6$ cm to $17.1$ cm. Regions near lines connecting microphones still have significantly larger uncertainty region.

To evaluate the array size's impact on accuracy, the size of the original array (as in fig~\ref{fig:sim_hm_3}) is increased by a factor of $2$. The result is presented in fig~\ref{fig:sim_hm_3_2x}. The overall uncertainty area decreased across the region. The average error improved to $10.04$ cm.

In fig~\ref{fig:sim_hm_3_line}, three microphones are placed $10$ cm apart from each other on the x-axis. Error heatmap shows high uncertainty on the x axis, and the overall accuracy is not as good as that with three microphones placed in a triangle. The average error is $55.05$ cm.

>>>>

\begin{figure}[]
  \centering
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/sim_2_1}
    \caption{source at $(r=50$ cm, $\theta = 0$ degrees$)$}
  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/sim_2_2}
    \caption{source at $(r=50$ cm, $\theta = 45$ degrees$)$}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/sim_2_3}
%    \caption{source at $(r=50$ cm, $\theta = 90$ degrees$)$}
%  \end{subfigure}
  \caption{Uncertainty region. Yellow dots represent microphones' locations and the white dot represents the location of the source.}
  \label{fig:sim_2_5}
\end{figure}

@@

\begin{figure*}[]
  \centering
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_20cm_0_degrees}
    \caption{0 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_20cm_45_degrees}
%    \caption{45 degrees}
%  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_20cm_90_degrees}
%    \caption{90 degrees}
%  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_20cm_135_degrees}
    \caption{135 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_20cm_180_degrees}
%    \caption{180 degrees}
%  \end{subfigure}
  \caption{Uncertainty region. Microphones are at the vertices of a $20$cm equilateral triangle. The source is $20$cm away from the array.}
  \label{fig:sim_3_2}
\end{figure*}

\begin{figure*}[]
  \centering
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_80cm_0_degrees}
    \caption{0 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_80cm_45_degrees}
%    \caption{45 degrees}
%  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_80cm_90_degrees}
%    \caption{90 degrees}
%  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_80cm_135_degrees}
    \caption{135 degrees}
  \end{subfigure}
%  \begin{subfigure}[]{.3\textwidth}
%    \includegraphics[width=\textwidth]{sim/result_80cm_180_degrees}
%    \caption{180 degrees}
%  \end{subfigure}
  \caption{Uncertainty region. Microphones are at the vertices of a $20$cm equilateral triangle. The source is $80$cm away from the array.}
  \label{fig:sim_3_8}
\end{figure*}

@@

\begin{figure*}[]
  \centering
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_center}
    \caption{$3$ microphones are placed at vertices of a $20$cm equilateral triangle. The average error is $18.6$ cm}
    \label{fig:sim_hm_3}
  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_p1}
    \caption{Another microphone is added at origin. The average error is $17.1$ cm}
    \label{fig:sim_hm_3_p1}
  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_2x}
    \caption{$3$ microphones are placed at vertices of a $40$cm equilateral triangle. The average error is $10.04$ cm}
    \label{fig:sim_hm_3_2x}
  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_3_line}
    \caption{$3$ microphones are placed in a line, $10$ cm apart from each other. The average error is $55.05$ cm}
    \label{fig:sim_hm_3_line}
  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_4corner}
    \caption{$4$ microphones are placed at $4$ corners of the grid. The average error is $0.05$ cm}
    \label{fig:sim_hm_4}
  \end{subfigure}
  \begin{subfigure}[]{.48\textwidth}
    \includegraphics[width=\textwidth]{sim/result_intersection_area_at_each_point_2a}
    \caption{Two $3$ microphone arrays are placed $1$ meter apart. The average error is $2.60$ cm}
    \label{fig:sim_hm_2_array}
  \end{subfigure}
  \caption{Error heatmap for different array configurations. The heatmap scale is the intersection area measured in $cm^2$}.
  \label{fig:sim_hm}
\end{figure*}

@@

To evaluate how adding one microphone (without increasing the array size) improves accuracy, another microphone is added to the array at $(0,0)$. Result is presented in fig~\ref{fig:sim_hm_3_p1}. Addition of the new microphone only slightly improved the accuracy around the array region. The average error dropped from $18.6$ cm to $17.1$ cm. Regions near lines connecting microphones still have significantly larger uncertainty region. This result suggests that adding more microphones in a small microphone array (without increasing the array size) is not an effective method to improve the localization accuracy.

To evaluate the array size's impact on accuracy, the size of the original array (as in fig~\ref{fig:sim_hm_3}) is increased by a factor of $2$. The result is presented in fig~\ref{fig:sim_hm_3_2x}. The overall uncertainty area decreased across the region. The average error improved to $10.04$ cm. By comparing with the previous result, it shows that increasing array size is more effective in improving accuracy than adding more microphones.

In fig~\ref{fig:sim_hm_3_line}, three microphones are placed $10$ cm apart from each other on the x-axis. Error heatmap shows high uncertainty on the x axis, and the overall accuracy much worse than that with three microphones placed in a triangle. The average error is $55.05$ cm.
